A generalized definition of multidimensional item response theory parameters

### 2023-02-15 output/paper_draft/paper_M2PLM_parameters.Rmd
agregados y coemntarios

@@

@@

>>>>

OBS. En la ecuación debe estar el producto inteno con el subindice que indique que es en la base B. No se ponen en las normas debido a la invarianza de estas. Como $\theta$ son las coordanadas en B se dejan igual.

@@

OBS en esta primera ecuación recordar poner el subindice B en el producto interno

@@

AGREGADO
Aca pongo redacciön alternativa dejo igual la origunal debajo

Before defining the multidimensional parameters, we need to make a clarification
regarding the representation of the items in the latent space.

We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of the discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces
Let us consider the model given by the equation (1 poner la referencia) where the latent traits and  the parameters $a_i$ are expressed in the same base B in their respective spaces.

We have  $\theta^{'}=P \theta$ so since the probability is invariant, the parameters $a_i$ must also be transformed in $a^{'}_i$.

Equating the probabilities we get $a_1^{'}=P^{-1^T}a_i=M^{-1}Pa_i$ .
This shows that first a base change to the standard base is performed and then a transformation through $M^{-1}$, so the $a^{'}_i$ are expressed in the standard base.

\begin{equation}
\|a_i^{'} \|=a_i^T P^{-1}P^{-1^T}a_i=a_i^TM^{-1}a_i
(\#eq:slope-param)
\end{equation}

Therefore, in the test space, a inner product matrix
$`r INNER_PROD_MATRIX_INV`$ can be defined,
such that $`r INNER_PROD_DISCR_EQ`$ to keep the norm invariant

Las vk no deben ir

Esta es la original
